Forecasting the old-age dependency ratio to determine the best pension age

### 2020-05-04 PensionAge.Rmd
Code styling

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = TRUE)
library(tidyverse)
library(demography)
#remotes::install_github("robjhyndman/addb")
library(addb)
library(patchwork)
library(kableExtra)
source("functions-v4.R")
source("hmd.R")
```

@@

```{r changespension, echo=FALSE, fig.cap="Government's adjustments on pension age scheme.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
# Policies obtained from https://www.dss.gov.au/seniors/benefits-payments/age-pension
# Law: https://guides.dss.gov.au/guide-social-security-law/3/4/1/10
# History: https://nationalseniors.com.au/news/campaign/a-short-history-of-the-age-pension-section
pension_age <- tibble(
    Year = 1920:2068,
    Current = 65
  ) %>%
  mutate(
    Proposed = pmin(70, Current + 0.5*pmax(0, trunc((Year - 2015)/2))),
    Approved = pmin(Proposed, 67),
  ) %>%
  pivot_longer(-Year, values_to="Age", names_to="Policy")

pension_age %>%
  filter(Year >= 2008, Year <= 2050) %>%
  ggplot(aes(x=Year, y=Age, group=Policy, col=Policy)) +
    geom_line() +
    ylab("Age of retirement") +
    scale_color_brewer(palette="Dark2",
      breaks = c("Proposed", "Approved", "Current"),
      labels = c("Proposed further change",  "Approved change", "Pension age at 65")
    )
```

@@

# Get population data to 1 Jan 2019
aus.pop <- hmd.pop(country = "AUS", username = username, password = password, label = "Australia")
aus.pop <- extract.ages(aus.pop, ages = 0:100)

@@

# Get fertility data for 1921-2006
aus.fert <- aus.fertility
births <- aus.fert$rate$female * aus.fert$pop$female
# Get latest fertility data from ABS (downloaded 30 April 2020)
ausf <- readr::read_csv("FERTILITY_AGE_STATE_30042020143630412.csv") %>%
  filter(
    Region == "Australia",
    Age %in% paste(15:49),
  ) %>%
  mutate(
    Year = Time,
    Age = as.numeric(Age)
  ) %>%
  select(Year, Age, Measure, Value)
# Extract births and population values
newbirths <- ausf %>%
  filter(Measure == "Births") %>%
  mutate(Value = Value * 1000) %>%
  select(-Measure) %>%
  pivot_wider(names_from=Year, values_from=Value) %>%
  select(-Age) %>%
  as.matrix()
newpop <- ausf %>%
  filter(Measure == "Female population") %>%
  mutate(Value = Value) %>%
  select(-Measure) %>%
  pivot_wider(names_from=Year, values_from=Value) %>%
  select(-Age) %>%
  as.matrix()
rownames(newbirths) <- rownames(newpop) <- 15:49

@@

# Compute migration data
aus.mig <- netmigration(mort = aus.mort, fert = aus.fert, startyearpop = aus.pop, mfratio = 1.05)
save(aus.fert, aus.mort, aus.mig, aus.pop, file="ausdata.Rdata")
rm(ausf,births,fpop,newbirths,newpop)
```

@@

```{r simulation, dependson='models'}
############### SIMULATION STEP #################
# This takes a while!
set.seed(2020-05-02)
nsim <- 20 # Change to 2000 or higher to get better estimates
aus.sim <- pop.sim(mort = mortf, fert = fertf, mig = migf, firstyearpop = aus.pop, N = nsim)

# Combine simulation results into one tibble
dimnames(aus.sim[["male"]]) <- dimnames(aus.sim[["female"]]) <- list(
  Age = dimnames(aus.sim[[1]])[[1]],
  Year = dimnames(aus.sim[[1]])[[2]],
  Rep = dimnames(aus.sim[[1]])[[3]]
)
aussim_df <- bind_rows(
  as.tbl_cube(aus.sim[["male"]]/1e3, met_name = "Population") %>%
    as_tibble() %>% mutate(Sex = "Male"),
  as.tbl_cube(aus.sim[["female"]]/1e3, met_name = "Population") %>%
    as_tibble() %>% mutate(Sex = "Female")
)
#rm(aus.sim)
# Combine simulations to create means and quantiles of future years
future_pop <- aussim_df %>%
  group_by(Sex, Age, Year) %>%
  summarise(
    Mean = mean(Population),
    Lower = quantile(Population, prob=0.1),
    Upper = quantile(Population, prob=0.9)
  ) %>%
  ungroup()
# Historical data as a tibble
history_pop <- bind_rows(
  as_tibble(aus.pop$pop$male / 1000) %>%
    mutate(
      Age = aus.pop$age,
      Sex = "Male"
    ) %>%
    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
  as_tibble(aus.pop$pop$female / 1000) %>%
    mutate(
      Age = aus.pop$age,
      Sex = "Female"
    ) %>%
    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
  ) %>%
  mutate(Year = as.numeric(Year))
```

```{r totalpopulationbyyears, fig.cap="Fifty-year forecasts of total population for each sex, along with 80% prediction intervals. The actually population from 1950 to 2015 is shown using circles.", fig.height=4, dependson='simulationresults'}
future_tot_pop <- aussim_df %>%
  group_by(Rep, Sex, Year) %>%
  summarise(Population = sum(Population)/1e3) %>%
  group_by(Sex, Year) %>%
  summarise(
    Mean = mean(Population),
    Median = median(Population),
    Lo95 = quantile(Population, prob=0.025),
    Up95 = quantile(Population, prob=0.975),
    Lo80 = quantile(Population, prob=0.1),
    Up80 = quantile(Population, prob=0.9)
  ) %>%
  ungroup()
history_pop %>%
  group_by(Sex, Year) %>%
  summarise(Population = sum(Population)/1e3) %>%
  ggplot(aes(x=Year, y=Population, group=Sex)) +
    geom_line(size=1) +
    ylab("Population (millions)") +
    ggtitle("Total population") +
    facet_grid(. ~ Sex) +
    geom_ribbon(aes(y=Mean, ymin=Lo80, ymax=Up80), fill='#7d7def', data=future_tot_pop) +
    geom_line(data=future_tot_pop, col='#0000cc', mapping=aes(y=Mean), size=1)
```

```{r totalpopulationin2034, fig.cap="Forecast population pyramid for 2034, along with 80% pointwise prediction intervals. The actual pyramid for 2015 is shown using dashed lines.", warnings=FALSE, dependson='simulationresults'}
pyramid <- function(history, future) {
  data <- bind_rows(history, future)
  p_male <- data %>%
    filter(Sex == "Male") %>%
    ggplot(aes(x = Age, y = Population, group=Year)) +
      labs(y = "Population ('000)") +
      geom_ribbon(aes(x=Age, ymin=Lower, ymax=Upper, y=Mean), fill='#7d7def') +
      geom_line(linetype=2) + geom_line(aes(y=Mean), col='#0000cc') +
      coord_flip() +
      scale_y_reverse(expand=c(0.012, 0.012)) +
      scale_x_continuous(expand=c(0.012,0.012)) +
      facet_grid(. ~ Sex)
  p_female <- data %>%
    filter(Sex == "Female") %>%
    ggplot(aes(x = Age, y = Population, group=Year)) +
      labs(y = "Population ('000)") +
      geom_ribbon(aes(x=Age, ymin=Lower, ymax=Upper, y=Mean), fill='#7d7def') +
      geom_line(linetype=2) + geom_line(aes(y=Mean), col='#0000cc') +
      coord_flip() +
      scale_y_continuous(expand=c(0.012,0.012)) +
      theme(axis.title.y.left=element_blank(),
        axis.text.y.left=element_blank(),
        axis.ticks.y.left=element_blank()) +
      scale_x_continuous(position="top", sec.axis = sec_axis(~ .), expand=c(0.012,0.012)) +
      facet_grid(. ~ Sex)

@@

```{r OADRat65, fig.cap="Fifty-year forecasts of the OADR with assumption of pension age equal to 65 for both sexes, along with 80% pointwise prediction interval.", dependson='simulationresults'}
OADR_history <- oadr(history_pop, filter(pension_age, Policy=='Current'))
OADR.65 <- oadr_sim(aussim_df, filter(pension_age, Policy=='Current')) %>%
  mutate(Policy="Pension age 65")
OADR.65 %>%
  ggplot(aes(x=Year, y=OADR)) +
    geom_ribbon(aes(ymin=Lo, ymax=Hi), fill='#7d7def') +
    geom_line(col='#0000aa', size=.75) +
    geom_line(col='black', size=.75, data=OADR_history) +
    xlab("year") + ylab("ratio") +
    ggtitle("OADR forecasts with pension age=65")
```

```{r OADRcurrent, fig.cap="Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green line) and equal to the pension age scheme with approved change (orange line) respectively, along with the desired OADR level in purple. The actual OADRs for 1950--2014 are shown in black.", dependson='OADRat65'}
df <- bind_rows(
  OADR.65,
  oadr_sim(aussim_df, filter(pension_age, Policy=='Approved')) %>%
    mutate(Policy="Current policy"),
  oadr_sim(aussim_df, filter(pension_age, Policy=='Proposed')) %>%
    mutate(Policy="Proposed policy")
) %>%
  mutate(Policy = factor(Policy,
    levels = c("Pension age 65","Current policy","Proposed policy")))
df %>%
  ggplot(aes(x=Year, y=OADR)) +
    geom_hline(yintercept = 0.21, col = "gray") +
    geom_ribbon(aes(ymin=Lo, ymax=Hi, fill=Policy, group=Policy), alpha=0.5) +
    geom_line(aes(col=Policy, group=Policy), size=.75) +
    geom_line(col='black', size=.75, data=OADR_history) +
    xlab("year") + ylab("ratio") +
    ggtitle("OADR forecasts with pension age=65") +
    scale_color_brewer(palette="Dark2") +
    scale_fill_brewer(palette="Dark2")
```

@@

```{r rollingtest, fig.cap="The mean absolute error of $h$-step-ahead forecast for $h=1,2,\\dots,25$.", warning=FALSE, message=FALSE, dependson='simulationresults'}
######## Run a rolling forecast origin
t <- 2014 - 1950 + 1
H <- 25 ## forecast horizon for test
k <- 25 ## years of data required to make a forecast
rolling_sim <- NULL
for (i in seq(t - k - H))
{
    ausmort.short <- extract.years(ausmort.sm, years = 1949 + i + (0:(k - 1)))
    ausfert.short <- extract.years(ausfert.sm, years = 1949 + i + (0:(k - 1)))
    ausmig.short <- extract.years(ausmig.sm, years = 1949 + i + (0:(k - 1)))
    pop.short <- extract.years(aus.pop, years = 1949 + i + (0:k))
    mort.fit.s <- coherentfdm(ausmort.short)
    mortfs <- forecast(mort.fit.s, H)
    fert.fit.s <- fdm(ausfert.short)
    # Fix problem
    #  miss <- is.na(fert.fit.s$residuals$y)
    #  fert.fit.s$residuals$y[miss] <- 0
    # End fix
    fertfs <- forecast(fert.fit.s, H)
    mig.fit.s <- coherentfdm(ausmig.short)
    migfs <- forecast(mig.fit.s, H)
    aus.sim.s <- pop.sim(mort = mortfs, fert = fertfs, mig = migfs,
                         firstyearpop = pop.short, N = 3)
    # Combine simulation results into one tibble
    dimnames(aus.sim.s[["male"]]) <-
      dimnames(aus.sim.s[["female"]]) <-
      list(
        Age = dimnames(aus.sim.s[[1]])[[1]],
        Year = dimnames(aus.sim.s[[1]])[[2]],
        Rep = dimnames(aus.sim.s[[1]])[[3]]
    )
    rolling_sim <- bind_rows(
      rolling_sim,
      as.tbl_cube(aus.sim.s[["male"]]/1e3, met_name = "Population") %>%
        as_tibble() %>% mutate(Sex = "Male", id=i),
      as.tbl_cube(aus.sim.s[["female"]]/1e3, met_name = "Population") %>%
        as_tibble() %>% mutate(Sex = "Female", id=i)
    )
}
```

```{r rmseplot, dependson="rollingtest"}
oadr_rolling_sim(rolling_sim,
    filter(pension_age, Policy=='Approved')) %>%
  group_by(id) %>%
  mutate(h = row_number()) %>%
  ungroup() %>%
  select(Year, h, OADR) %>%
  rename(Forecast = OADR) %>%
  left_join(OADR_history, by="Year") %>%
  mutate(e = OADR-Forecast) %>%
  group_by(h) %>%
  summarise(RMSE = sqrt(mean(e^2))) %>%
  ggplot(aes(x=h, y=RMSE)) +
    geom_point()
```

@@

# Lower bound (starting at age 65)
pension_age_lower <- pension_age %>%
  filter(Policy == "Current", Year >= 2019) %>% select(-Policy)
for (i in seq(5,50)) {
  current <- oadr_sim(aussim_df, pension_age_lower)$Lo[i]
  while ((current > target) &
         (max(diff(pension_age_lower$Age[(i-1):50])) <= (1 - 1/12))) {
    pension_age_lower$Age[i:50] <- pension_age_lower$Age[i:50] + 1/12
    current <- oadr_sim(aussim_df, pension_age_lower)$Lo[i]
  }
}
# Mean (start at lower bound)
pension_age_optimal <- pension_age_lower
for (i in seq(5,50)) {
  current <- oadr_sim(aussim_df, pension_age_optimal)$OADR[i]
  while ((current > target) &
         (max(diff(pension_age_optimal$Age[(i-1):50])) <= (1 - 1/12))) {
    pension_age_optimal$Age[i:50] <- pension_age_optimal$Age[i:50] + 1/12
    current <- oadr_sim(aussim_df, pension_age_optimal)$OADR[i]
  }
}
# Upper bound (start at mean)
pension_age_upper <- pension_age_optimal
for (i in seq(5,50)) {
  current <- oadr_sim(aussim_df, pension_age_upper)$Hi[i]
  while ((current > target) &
         (max(diff(pension_age_upper$Age[(i-1):50])) <= (1 - 1/12))) {
    pension_age_upper$Age[i:50] <- pension_age_upper$Age[i:50] + 1/12
    current <- oadr_sim(aussim_df, pension_age_upper)$Hi[i]
  }
}
# Final results
OADR_optimal <- oadr_sim(aussim_df, pension_age_optimal)
pension_age_optimal <- pension_age_optimal %>%
  mutate(
    Lo80 = pension_age_lower$Age,
    Hi80 = pension_age_upper$Age
  )
```

@@

```{r pensionagetables, dependson="optimal_pension", message=FALSE}
pension_age_optimal %>%
  mutate(
    Month = round((Age - trunc(Age)) * 12),
    Agestring = paste0(trunc(Age),"Y",
      if_else(Month > 0, paste0("+", Month, "M"), "")),
    Column = trunc((Year - 2019) / 10) + 1,
  ) %>%
  select(Year, Agestring, Column) %>%
  nest(data=c(Year=Year, Age=Agestring)) %>%
  pivot_wider(names_from=Column, values_from=data) %>%
  unnest(cols=paste(1:5), names_repair='unique') %>%
  knitr::kable(
    format="latex",
    col.names = rep(c("Year","Age"),5),
    booktabs = TRUE,
    caption = "Fifty-year target pension age scheme with stable OADR around desired OADR. Y denotes years and M denotes months."
  )
```

```{r pensionagetables2, dependson="OADRat65"}
pension_age_optimal %>%
  mutate(
    MonthLo = round((Lo80 - trunc(Lo80)) * 12),
    MonthHi = round((Hi80 - trunc(Hi80)) * 12),
    AgeLo = paste0(trunc(Lo80),"Y",
      if_else(MonthLo > 0, paste0("+", MonthLo, "M"), "")),
    AgeHi = paste0(trunc(Hi80),"Y",
      if_else(MonthHi > 0, paste0("+", MonthHi, "M"), "")),
    Column = trunc((Year - 2019) / 10) + 1,
  ) %>%
  select(Year, AgeLo, AgeHi, Column) %>%
  nest(data=c(Year=Year, Lo=AgeLo, Hi = AgeHi)) %>%
  pivot_wider(names_from=Column, values_from=data) %>%
  unnest(cols=paste(1:5), names_repair='unique') %>%
  knitr::kable(
    format="latex",
    col.names = rep(c("Year","Lo","Hi"),5),
    booktabs = TRUE,
    caption = "Fifty-year lower and higher boundary of pension age scheme with 80\\% confidence. Y denotes years and M denotes months."
  )
kable_styling(kable_output, font_size = 7)
```

```{r OADRwithoptimal, fig.cap="The mean forecast of OADR associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2014). The 80% prediction interval of the forecast of OADR is shown as blue shading.", dependson="OADRat65"}
## plots of OADR with plausible pension age schemes
OADR_optimal %>%
  ggplot(aes(x=Year)) +
  geom_ribbon(aes(ymin=Lo, ymax=Hi), fill="#7d7def") +

autoplot(OADR.f.optimal$x) +
  geom_hline(yintercept = OADR.f$mean[4], col = "red") +
  autolayer(OADR.f.optimal) +
  ggtitle("OADR forecast estimates for optimal pension ages") +
  xlab("year") + ylab("ratio")
```

@@

```{r ComparisonwithOADR22, fig.cap="The comparison between the target pension age scheme (in green) associated with desired level equal to current level plus $1%$ (i.e., 22%) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade.", dependson="OADRat65"}
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = TRUE)
library(tidyverse)
library(demography)
# remotes::install_github("robjhyndman/addb")
library(addb)
library(patchwork)
library(kableExtra)
source("functions-v4.R")
```

@@

```{r changespension, echo=FALSE, fig.cap="Government's adjustments on pension age scheme.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
# Policies obtained from https://www.dss.gov.au/seniors/benefits-payments/age-pension
# Law: https://guides.dss.gov.au/guide-social-security-law/3/4/1/10
# History: https://nationalseniors.com.au/news/campaign/a-short-history-of-the-age-pension-section
pension_age <- tibble(
  Year = 1920:2068,
  Current = 65
) %>%
  mutate(
    Proposed = pmin(70, Current + 0.5 * pmax(0, trunc((Year - 2015) / 2))),
    Approved = pmin(Proposed, 67),
  ) %>%
  pivot_longer(-Year, values_to = "Age", names_to = "Policy")

pension_age %>%
  filter(Year >= 2008, Year <= 2050) %>%
  ggplot(aes(x = Year, y = Age, group = Policy, col = Policy)) +
  geom_line() +
  ylab("Age of retirement") +
  scale_color_brewer(
    palette = "Dark2",
    breaks = c("Proposed", "Approved", "Current"),
    labels = c("Proposed further change", "Approved change", "Pension age at 65")
  )
```

@@

# Get population data to 1 Jan 2019
source("hmd.R") # File only stores username and password
aus.pop <- hmd.pop(
  country = "AUS", username = username, password = password,
  label = "Australia"
)
aus.pop <- extract.ages(aus.pop, ages = 0:100)

@@

# Get fertility data for 1921-2006
aus.fert <- aus.fertility
births <- aus.fert$rate$female * aus.fert$pop$female
# Get latest fertility data from ABS (downloaded 30 April 2020)
ausf <- readr::read_csv("FERTILITY_AGE_STATE_30042020143630412.csv") %>%
  filter(
    Region == "Australia",
    Age %in% paste(15:49),
  ) %>%
  mutate(
    Year = Time,
    Age = as.numeric(Age)
  ) %>%
  select(Year, Age, Measure, Value)
# Extract births and population values
newbirths <- ausf %>%
  filter(Measure == "Births") %>%
  mutate(Value = Value * 1000) %>%
  select(-Measure) %>%
  pivot_wider(names_from = Year, values_from = Value) %>%
  select(-Age) %>%
  as.matrix()
newpop <- ausf %>%
  filter(Measure == "Female population") %>%
  mutate(Value = Value) %>%
  select(-Measure) %>%
  pivot_wider(names_from = Year, values_from = Value) %>%
  select(-Age) %>%
  as.matrix()
rownames(newbirths) <- rownames(newpop) <- 15:49

@@

# Compute migration data
aus.mig <- netmigration(
  mort = aus.mort, fert = aus.fert,
  startyearpop = aus.pop, mfratio = 1.05
)
save(aus.fert, aus.mort, aus.mig, aus.pop, file = "ausdata.Rdata")
rm(ausf, births, fpop, newbirths, newpop)
```

@@

```{r simulation, dependson='models'}
############### SIMULATION STEP #################
# This takes a while!
set.seed(2020 - 05 - 02)
nsim <- 20 # Change to 2000 or higher to get better estimates
aus.sim <- pop.sim(mort = mortf, fert = fertf, mig = migf, firstyearpop = aus.pop, N = nsim)

# Combine simulation results into one tibble
dimnames(aus.sim[["male"]]) <- dimnames(aus.sim[["female"]]) <- list(
  Age = dimnames(aus.sim[[1]])[[1]],
  Year = dimnames(aus.sim[[1]])[[2]],
  Rep = dimnames(aus.sim[[1]])[[3]]
)
aussim_df <- bind_rows(
  as.tbl_cube(aus.sim[["male"]] / 1e3, met_name = "Population") %>%
    as_tibble() %>% mutate(Sex = "Male"),
  as.tbl_cube(aus.sim[["female"]] / 1e3, met_name = "Population") %>%
    as_tibble() %>% mutate(Sex = "Female")
)
# rm(aus.sim)
# Combine simulations to create means and quantiles of future years
future_pop <- aussim_df %>%
  group_by(Sex, Age, Year) %>%
  summarise(
    Mean = mean(Population),
    Lower = quantile(Population, prob = 0.1),
    Upper = quantile(Population, prob = 0.9)
  ) %>%
  ungroup()
# Historical data as a tibble
history_pop <- bind_rows(
  as_tibble(aus.pop$pop$male / 1000) %>%
    mutate(
      Age = aus.pop$age,
      Sex = "Male"
    ) %>%
    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
  as_tibble(aus.pop$pop$female / 1000) %>%
    mutate(
      Age = aus.pop$age,
      Sex = "Female"
    ) %>%
    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
) %>%
  mutate(Year = as.numeric(Year))
```

```{r totalpopulationbyyears, fig.cap="Fifty-year forecasts of total population for each sex, along with 80% prediction intervals. The actually population from 1950 to 2015 is shown using circles.", fig.height=4, dependson='simulationresults'}
future_tot_pop <- aussim_df %>%
  group_by(Rep, Sex, Year) %>%
  summarise(Population = sum(Population) / 1e3) %>%
  group_by(Sex, Year) %>%
  summarise(
    Mean = mean(Population),
    Median = median(Population),
    Lo95 = quantile(Population, prob = 0.025),
    Up95 = quantile(Population, prob = 0.975),
    Lo80 = quantile(Population, prob = 0.1),
    Up80 = quantile(Population, prob = 0.9)
  ) %>%
  ungroup()
history_pop %>%
  group_by(Sex, Year) %>%
  summarise(Population = sum(Population) / 1e3) %>%
  ggplot(aes(x = Year, y = Population, group = Sex)) +
  geom_line(size = 1) +
  ylab("Population (millions)") +
  ggtitle("Total population") +
  facet_grid(. ~ Sex) +
  geom_ribbon(aes(y = Mean, ymin = Lo80, ymax = Up80), fill = "#7d7def", data = future_tot_pop) +
  geom_line(data = future_tot_pop, col = "#0000cc", mapping = aes(y = Mean), size = 1)
```

```{r totalpopulationin2034, fig.cap="Forecast population pyramid for 2034, along with 80% pointwise prediction intervals. The actual pyramid for 2015 is shown using dashed lines.", warnings=FALSE, dependson='simulationresults'}
pyramid <- function(history, future) {
  data <- bind_rows(history, future)
  p_male <- data %>%
    filter(Sex == "Male") %>%
    ggplot(aes(x = Age, y = Population, group = Year)) +
    labs(y = "Population ('000)") +
    geom_ribbon(aes(x = Age, ymin = Lower, ymax = Upper, y = Mean), fill = "#7d7def") +
    geom_line(linetype = 2) +
    geom_line(aes(y = Mean), col = "#0000cc") +
    coord_flip() +
    scale_y_reverse(expand = c(0.012, 0.012)) +
    scale_x_continuous(expand = c(0.012, 0.012)) +
    facet_grid(. ~ Sex)
  p_female <- data %>%
    filter(Sex == "Female") %>%
    ggplot(aes(x = Age, y = Population, group = Year)) +
    labs(y = "Population ('000)") +
    geom_ribbon(aes(x = Age, ymin = Lower, ymax = Upper, y = Mean), fill = "#7d7def") +
    geom_line(linetype = 2) +
    geom_line(aes(y = Mean), col = "#0000cc") +
    coord_flip() +
    scale_y_continuous(expand = c(0.012, 0.012)) +
    theme(
      axis.title.y.left = element_blank(),
      axis.text.y.left = element_blank(),
      axis.ticks.y.left = element_blank()
    ) +
    scale_x_continuous(position = "top", sec.axis = sec_axis(~.), expand = c(0.012, 0.012)) +
    facet_grid(. ~ Sex)

@@

```{r OADRat65, fig.cap="Fifty-year forecasts of the OADR with assumption of pension age equal to 65 for both sexes, along with 80% pointwise prediction interval.", dependson='simulationresults'}
OADR_history <- oadr(history_pop, filter(pension_age, Policy == "Current"))
OADR.65 <- oadr_sim(aussim_df, filter(pension_age, Policy == "Current")) %>%
  mutate(Policy = "Pension age 65")
OADR.65 %>%
  ggplot(aes(x = Year, y = OADR)) +
  geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
  geom_line(col = "#0000aa", size = .75) +
  geom_line(col = "black", size = .75, data = OADR_history) +
  xlab("year") +
  ylab("ratio") +
  ggtitle("OADR forecasts with pension age=65")
```

```{r OADRcurrent, fig.cap="Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green line) and equal to the pension age scheme with approved change (orange line) respectively, along with the desired OADR level in purple. The actual OADRs for 1950--2014 are shown in black.", dependson='OADRat65'}
df <- bind_rows(
  OADR.65,
  oadr_sim(aussim_df, filter(pension_age, Policy == "Approved")) %>%
    mutate(Policy = "Current policy"),
  oadr_sim(aussim_df, filter(pension_age, Policy == "Proposed")) %>%
    mutate(Policy = "Proposed policy")
) %>%
  mutate(Policy = factor(Policy,
    levels = c("Pension age 65", "Current policy", "Proposed policy")
  ))
df %>%
  ggplot(aes(x = Year, y = OADR)) +
  geom_hline(yintercept = 0.21, col = "gray") +
  geom_ribbon(aes(ymin = Lo, ymax = Hi, fill = Policy, group = Policy), alpha = 0.5) +
  geom_line(aes(col = Policy, group = Policy), size = .75) +
  geom_line(col = "black", size = .75, data = OADR_history) +
  xlab("year") +
  ylab("ratio") +
  ggtitle("OADR forecasts with pension age=65") +
  scale_color_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2")
```

@@

```{r rollingtest, fig.cap="The mean absolute error of $h$-step-ahead forecast for $h=1,2,\\dots,25$.", warning=FALSE, message=FALSE, dependson='simulationresults'}
######## Run a rolling forecast origin
t <- 2014 - 1950 + 1
H <- 25 ## forecast horizon for test
k <- 25 ## years of data required to make a forecast
rolling_sim <- NULL
for (i in seq(t - k - H))
{
  ausmort.short <- extract.years(ausmort.sm, years = 1949 + i + (0:(k - 1)))
  ausfert.short <- extract.years(ausfert.sm, years = 1949 + i + (0:(k - 1)))
  ausmig.short <- extract.years(ausmig.sm, years = 1949 + i + (0:(k - 1)))
  pop.short <- extract.years(aus.pop, years = 1949 + i + (0:k))
  mort.fit.s <- coherentfdm(ausmort.short)
  mortfs <- forecast(mort.fit.s, H)
  fert.fit.s <- fdm(ausfert.short)
  # Fix problem
  #  miss <- is.na(fert.fit.s$residuals$y)
  #  fert.fit.s$residuals$y[miss] <- 0
  # End fix
  fertfs <- forecast(fert.fit.s, H)
  mig.fit.s <- coherentfdm(ausmig.short)
  migfs <- forecast(mig.fit.s, H)
  aus.sim.s <- pop.sim(
    mort = mortfs, fert = fertfs, mig = migfs,
    firstyearpop = pop.short, N = 3
  )
  # Combine simulation results into one tibble
  dimnames(aus.sim.s[["male"]]) <-
    dimnames(aus.sim.s[["female"]]) <-
    list(
      Age = dimnames(aus.sim.s[[1]])[[1]],
      Year = dimnames(aus.sim.s[[1]])[[2]],
      Rep = dimnames(aus.sim.s[[1]])[[3]]
    )
  rolling_sim <- bind_rows(
    rolling_sim,
    as.tbl_cube(aus.sim.s[["male"]] / 1e3, met_name = "Population") %>%
      as_tibble() %>% mutate(Sex = "Male", id = i),
    as.tbl_cube(aus.sim.s[["female"]] / 1e3, met_name = "Population") %>%
      as_tibble() %>% mutate(Sex = "Female", id = i)
  )
}
```

```{r rmseplot, dependson="rollingtest"}
oadr_rolling_sim(
  rolling_sim,
  filter(pension_age, Policy == "Approved")
) %>%
  group_by(id) %>%
  mutate(h = row_number()) %>%
  ungroup() %>%
  select(Year, h, OADR) %>%
  rename(Forecast = OADR) %>%
  left_join(OADR_history, by = "Year") %>%
  mutate(e = OADR - Forecast) %>%
  group_by(h) %>%
  summarise(RMSE = sqrt(mean(e^2))) %>%
  ggplot(aes(x = h, y = RMSE)) +
  geom_point()
```

@@

# Lower bound (starting at age 65)
pension_age_lower <- pension_age %>%
  filter(Policy == "Current", Year >= 2019) %>%
  select(-Policy)
for (i in seq(5, 50)) {
  current <- oadr_sim(aussim_df, pension_age_lower)$Lo[i]
  while ((current > target) &
    (max(diff(pension_age_lower$Age[(i - 1):50])) <= (1 - 1 / 12))) {
    pension_age_lower$Age[i:50] <- pension_age_lower$Age[i:50] + 1 / 12
    current <- oadr_sim(aussim_df, pension_age_lower)$Lo[i]
  }
}
# Mean (start at lower bound)
pension_age_optimal <- pension_age_lower
for (i in seq(5, 50)) {
  current <- oadr_sim(aussim_df, pension_age_optimal)$OADR[i]
  while ((current > target) &
    (max(diff(pension_age_optimal$Age[(i - 1):50])) <= (1 - 1 / 12))) {
    pension_age_optimal$Age[i:50] <- pension_age_optimal$Age[i:50] + 1 / 12
    current <- oadr_sim(aussim_df, pension_age_optimal)$OADR[i]
  }
}
# Upper bound (start at mean)
pension_age_upper <- pension_age_optimal
for (i in seq(5, 50)) {
  current <- oadr_sim(aussim_df, pension_age_upper)$Hi[i]
  while ((current > target) &
    (max(diff(pension_age_upper$Age[(i - 1):50])) <= (1 - 1 / 12))) {
    pension_age_upper$Age[i:50] <- pension_age_upper$Age[i:50] + 1 / 12
    current <- oadr_sim(aussim_df, pension_age_upper)$Hi[i]
  }
}
# Final results
OADR_optimal <- oadr_sim(aussim_df, pension_age_optimal)
pension_age_optimal <- pension_age_optimal %>%
  mutate(
    Lo80 = pension_age_lower$Age,
    Hi80 = pension_age_upper$Age
  )
```

@@

```{r pensionagetables, dependson="optimal_pension", message=FALSE}
pension_age_optimal %>%
  mutate(
    Month = round((Age - trunc(Age)) * 12),
    Agestring = paste0(
      trunc(Age), "Y",
      if_else(Month > 0, paste0("+", Month, "M"), "")
    ),
    Column = trunc((Year - 2019) / 10) + 1,
  ) %>%
  select(Year, Agestring, Column) %>%
  nest(data = c(Year = Year, Age = Agestring)) %>%
  pivot_wider(names_from = Column, values_from = data) %>%
  unnest(cols = paste(1:5), names_repair = "unique") %>%
  knitr::kable(
    format = "latex",
    col.names = rep(c("Year", "Age"), 5),
    booktabs = TRUE,
    caption = "Fifty-year target pension age scheme with stable OADR around desired OADR. Y denotes years and M denotes months."
  )
```

```{r pensionagetables2, dependson="OADRat65"}
pension_age_optimal %>%
  mutate(
    MonthLo = round((Lo80 - trunc(Lo80)) * 12),
    MonthHi = round((Hi80 - trunc(Hi80)) * 12),
    AgeLo = paste0(
      trunc(Lo80), "Y",
      if_else(MonthLo > 0, paste0("+", MonthLo, "M"), "")
    ),
    AgeHi = paste0(
      trunc(Hi80), "Y",
      if_else(MonthHi > 0, paste0("+", MonthHi, "M"), "")
    ),
    Column = trunc((Year - 2019) / 10) + 1,
  ) %>%
  select(Year, AgeLo, AgeHi, Column) %>%
  nest(data = c(Year = Year, Lo = AgeLo, Hi = AgeHi)) %>%
  pivot_wider(names_from = Column, values_from = data) %>%
  unnest(cols = paste(1:5), names_repair = "unique") %>%
  knitr::kable(
    format = "latex",
    col.names = rep(c("Year", "Lo", "Hi"), 5),
    booktabs = TRUE,
    caption = "Fifty-year lower and higher boundary of pension age scheme with 80\\% confidence. Y denotes years and M denotes months."
  )
kable_styling(kable_output, font_size = 7)
```

```{r OADRwithoptimal, fig.cap="The mean forecast of OADR associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2014). The 80% prediction interval of the forecast of OADR is shown as blue shading.", dependson="OADRat65"}
## plots of OADR with plausible pension age schemes
OADR_optimal %>%
  ggplot(aes(x = Year)) +
  geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
  autoplot(OADR.f.optimal$x) +
  geom_hline(yintercept = OADR.f$mean[4], col = "red") +
  autolayer(OADR.f.optimal) +
  ggtitle("OADR forecast estimates for optimal pension ages") +
  xlab("year") +
  ylab("ratio")
```

@@

```{r ComparisonwithOADR22, fig.cap="The comparison between the target pension age scheme (in green) associated with desired level equal to current level plus $1%$ (i.e., 22%) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade.", dependson="OADRat65"}

```
